Multi-wavelength Radio Continuum Emission Studies of Dust-free Red Giants

### 2013-04-03 draft_06/draft.tex
A few edits from Rathmines

\begin{figure}
\includegraphics[trim = 5mm 0mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
\caption{Predicted effective radius (dashed lines) as a function of wavelength for $\alpha$ Boo and $\alpha$ Tau. Points corresponding to our long wavelength VLA measurements are also shown.  At the same radio wavelengths the less ionized and less opaque mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
\label{fig:fig5}
\end{figure}

>>>>

\begin{figure}
\includegraphics[trim = 5mm 0mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
\caption{Predicted effective radius (dashed lines) as a function of wavelength derived from the existing atmospheric models of $\alpha$ Boo and $\alpha$ Tau.  Also plotted is the predicted effective radius derived from our analytical advection model discussed in \ref{disc:disc4}. Points corresponding to our long wavelength VLA measurements are also shown. At the same radio wavelengths the less ionized and less opaque mass outflow of  Tau results in a smaller effective radius than $\alpha$ Boo.}
\label{fig:fig5}
\end{figure}
